\subsection{ITN LIKE Poster session}

The ITN LIKE early-stage researchers provided a quick overview of their work in the plenum session, before splitting in to individual breakout rooms to discuss their work in detail.  

\begin{itemize}
\item Shahbaz Pathan, DTU Wind Energy, Denmark.
\item Liqin Jin, DTU Wind Energy, Denmark.
\item Francisco Costa, University of Stuttgart.
\item Hugo Rubio Hurtado, Fraunhofer Institute for Wind Energy Systems, University of Oldenburg.
\item Isadora Limas Coimbra, University of Porto, Faculty of Engineering.
\item Haichen Zuo, DTU Wind Energy, Denmark.
\item Jan Markus Diezel, Geophysical Institute, University of Bergen, Norway.
\item Priscila Suarez Orozco, UL International GmbH.
\item Arjun Anantharaman, Center for Wind energy research, University of Oldenburg.
\item Alessandro Sebastiani, DTU Wind Energy, Denmark.
\item Feng Guo, Flensburg University of Applied Sciences.
\item Wei Fu, DTU Wind Energy, Denmark.
\item Mohammad Nafisifard, Department of Mechanical and Structural Engineering and Material Science, University of Stavanger.
\item Zhaoyu Zhang, Department of Mechanical Engineering, Politecnico di Milano.
\item Sai Wang, University of Bergen, Norway.
\end{itemize}

More information about the ESRs and their projects are available at \href{https://www.msca-like.eu/People}{www.msca-like.eu/people}. 

\faFilePowerpointO~ Find the presentation about the ESRs and their research interests at \href{https://doi.org/10.5281/zenodo.5726900
}{DOI: 10.5281/zenodo.5726900}. 

The meeting adjourned at 16:45 CET.